A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-06-13 crystal-gel/presentation/talk_Roscoff.tex
biblio crystal-gel
experimental slide

\begin{columns}
	\column{0.45\textwidth}
	\begin{tikzpicture}
		\let\mrad\relax
		\newlength\mrad
		\setlength{\mrad}{1em}

@@

		\node[text width=6em, anchor=base east, inner xsep=0,xshift=1.5\mrad, align=right] (coll) at (colli.east|-pur.base) {depletion};
	\end{tikzpicture}

	\bigskip
	\includegraphics[width=\textwidth]{/home/mathieu/Documents/Recherches/tex/CNRS-2015/Renth_sedim.jpg}\\
	\textit{\footnotesize Renth 1999}
	\begin{itemize}
	\item triple coexistence
	\item various kinetic paths
	\end{itemize}

@@

>>>>

\begin{columns}
	\column{0.45\textwidth}
	\tikzsetnextfilename{interactions}%
	\begin{tikzpicture}
		\let\mrad\relax
		\newlength\mrad
		\setlength{\mrad}{1em}

@@

		\node[text width=6em, anchor=base east, inner xsep=0,xshift=1.5\mrad, align=right] (coll) at (colli.east|-pur.base) {depletion};
	\end{tikzpicture}\\

	\bigskip
	\includegraphics[width=\textwidth]{../../CNRS-2015/Renth_sedim.jpg}\\
	\textit{\footnotesize Poon PRL 1999, Renth PRE 2001}
	\begin{itemize}
	\item triple coexistence
	\item various kinetic paths
	\end{itemize}

@@

\begin{frame}{Another class of gel? Crystal-gel?}
	\begin{itemize}
	\item Phase separation arrested by crystallisation
	\begin{description}
		\item[polymer blend] Tanaka \& Nishi \textit{PRL} 1985
		\item[simulations] Soga \textit{J.Chem. Phys.} 1999; Fortini \textit{PRE} 2008 
	\end{description}
	\item Spinodal then crystallisation
	\begin{description}
		\item[simulations] Pérez \textit{Langmuir} 2011
		\item[microgravity] (triple coexistence) Sabin \textit{PRL} 2012
	\end{description}
	\end{itemize}
	\includegraphics[width=\textwidth]{micrograv_Sabin2012}
\end{frame}

\begin{frame}{Experimental}
How to do that in 3D at particle level \alert{without a space station}?
\begin{itemize}
\item index matched + \alert{\SI{2.3}{\micro\metre} colloids} + confocal
\item density match + $T$-control
\item preparation protocol without flow
\end{itemize}
\bigskip
\begin{columns}
	\column{0.265\textwidth}
		Colloids+polymers\\
		{\footnotesize no screening
		\begin{itemize}
			\item Dispersed
			\item Homogeneous
		\end{itemize}
		\bigskip
		\begin{beamercolorbox}[rounded=true]{block body}PMMA + PS\\
		in decalin + CHB $\epsilon_r\approx5$\\
		$\kappa^{-1}>\SI{10}{\micro\metre}$
		\end{beamercolorbox}}
	\column{0.4\textwidth}
		\tikzsetnextfilename{chemin_gelification}%
		\input{chemin_gelification.pgf}
	\column{0.335\textwidth}
		\tikzsetnextfilename{cell}%
		\input{cell.pgf}
\end{columns}
\end{frame}
